\documentclass[11pt]{article}
\usepackage{amssymb}
\usepackage{url}
\usepackage{color}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{graphics,epsfig,cite,subfigure,amsmath,xspace}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\definecolor{darkblue}{rgb}{0, 0, .6}
\definecolor{grey}{rgb}{.7, .7, .7}
\usepackage[breaklinks]{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=darkblue,
	anchorcolor=darkblue,
	citecolor=darkblue,
	pagecolor=darkblue,
	urlcolor=darkblue,
	pdftitle={},
	pdfauthor={}
}

\begin{document}

\begin{center}
{\Large \textbf{Collaborative Research: Resource of Open\\
Problems for Education (ROPE)}}

\bigskip

{\Large Biographical Sketch}\\
\smallskip
Spencer Hamblen
\end{center}

\begin{enumerate}[leftmargin=*]

\item[(a)] \textbf{Professional Preparation}

\begin{tabularx}{6.4in}{XXX}
Amherst College  & Mathematics and Women's and Gender Studies & \hfill BA, 1998\\
Cornell University & Mathematics & \hfill PhD, 2005 \\
Queen's University & Mathematics & \hfill Postdoctoral, 2005 to 2007\\
\end{tabularx}

\item[(b)] \textbf{Appointments}

Assistant Professor, McDaniel College  \hfill 2007 to 2013\\
Associate Professor, McDaniel College  \hfill 2013 to present\\



\item[(c)] \textbf{Products}


S.~Hamblen.  Lifting $n$-dimensional Galois representations. {\em Canadian Journal of Mathematics}, vol. 60, no. 5, (2008), 1028-1049.

\smallskip

S.~Hamblen, R.~Ramakrishna.  Deformations of certain reducible Galois representations II. {\em American Journal of Mathematics}, vol. 130, no. 4, (2008), 913-944.

\smallskip

S.~Hamblen, R.~Jones, K.~Madhu. The Density of Primes in Orbits of $z^d + c$.  {\em International Mathematics Research Notices}, to appear.  [\href{http://arxiv.org/abs/1303.6513}{\texttt{arXiv:1303.6513}}]


 
\item[(d)] \textbf{Synergistic Activities}

Contributor to GoodQuestions project \hfill Spring 2004\\
(http://www.math.cornell.edu/~GoodQuestions/)


\item[(e)] \textbf{Collaborators and Other Affiliations} 
 
Rafe Jones (Carleton College)

Kalyani Madhu (University of Rochester)

Colleen Duffy (University of Wisconsin-Eau Claire)

Kate Petersen (Florida State University)

Ravi Ramakrishna (Cornell University)

Ben Steinhurst (McDaniel College)

\end{enumerate}

\end{document}