\documentclass[11pt]{article}

\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\definecolor{darkblue}{rgb}{0, 0, .6}
\usepackage[breaklinks]{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=darkblue,
	anchorcolor=darkblue,
	citecolor=darkblue,
	pagecolor=darkblue,
	urlcolor=darkblue,
	pdftitle={},
	pdfauthor={}
}

\linespread{1.2}

\begin{document}

\begin{center}
{\Large \textbf{Collaborative Research: Resource of Open\\
Problems for Education (ROPE)}}

\bigskip

{\Large Biographical Sketch}\\
\vspace{.25em}
Dana C.~Ernst
\end{center}

\begin{enumerate}[leftmargin=*]

\item[(a)] \textbf{Professional Preparation}

\begin{tabularx}{6.4in}{@{}XX}
George Mason University  & Mathematics \hfill BS, 1997\\
Northern Arizona University & Mathematics \hfill MS, 2000\\
University of Colorado at Boulder & Mathematics \hfill PhD, 2008
\end{tabularx}

\item[(b)] \textbf{Appointments}

Northern Arizona University, Flagstaff, AZ\\
Assistant Professor, Mathematics \& Statistics Department  \hfill Aug 2012--Present

\vspace{.25em}

Plymouth State University, Plymouth, NH\\
Assistant Professor, Mathematics Department  \hfill Aug 2008--May 2012
 
%\vspace{.25em}
%
%University of Colorado at Boulder, Boulder, CO\\  
%Graduate Teaching Instructor, Department of Mathematics  \hfill Aug 2003--May 2008

%Research Fellow, Thron Fellowship \hfill Summer 2007\\
%Lead Graduate Teacher, Graduate Teacher Program \hfill Aug 2006--May 2007

%\vspace{.25em}
%
%Front Range Community College, Boulder, CO\\
%Full-time Faculty, Department of Mathematics \hfill Aug 2001--May 2003

%\vspace{.25em}
%
%Northern Arizona University, Flagstaff, AZ\\
%Full-time Instructor, Department of Mathematics \& Statistics \hfill Jun 2000--May 2001\\
%Graduate Teaching Instructor, Department of Mathematics \& Statistics \hfill Aug 1997--May 2000

\item[(c)] \textbf{Products}

\begin{enumerate}[leftmargin=\parindent]
\item[(i)] \textbf{Most closely related to project}

D.C.~Ernst, A.~Hodge, and A.~Schultz.  Enhancing Proof Writing via Cross-Institutional Peer Review. Accepted to \emph{PRIMUS}.

\vspace{.25em}

B.~Beaudrie, D.C.~Ernst, and B.~Boschmans. Redesigning an Algebra for Precalculus Course. In T.~Bastiaens \& G.~Marks (Eds.), Proceedings of World Conference on E-Learning in Corporate, Government, Healthcare, and Higher Education, 2013. Chesapeake, VA: AACE. [\href{http://www.editlib.org/p/115001/}{\texttt{EdITLib:115001}}]

\vspace{.25em}

B.~Beaudrie, D.C.~Ernst, and B.~Boschmans. First Semester Experiences in Implementing a Mathematics Emporium Model. In R.~McBride \& M.~Searson (Eds.), \emph{Proceedings of Society for Information Technology \& Teacher Education International Conference}, 2013.  New Orleans, LA: AACE.  [\href{http://www.editlib.org/p/48098}{\texttt{EdITLib:48098}}]

\vspace{.25em}

D.C.~Ernst. \emph{An Introduction to Proof via Inquiry-Based Learning}.  IBL course materials for an introduction to proof course. [\href{http://dcernst.github.io/IBL-IntroToProof}{\texttt{dcernst.github.io/IBL-IntroToProof}}]

\vspace{.25em}

D.C.~Ernst. \emph{An Inquiry-Based Approach to Abstract Algebra}.  IBL course materials for an abstract algebra course. [\href{http://dcernst.github.io/IBL-AbstractAlgebra}{\texttt{dcernst.github.io/IBL-AbstractAlgebra}}]
 
\item[(ii)] \textbf{Additional}

D.C.~Ernst and N. Sieben. Impartial achievement and avoidance games for generating finite groups. [\href{http://arxiv.org/abs/1407.0784}{\texttt{arXiv:1407.0784}}]

\vspace{.25em}

T.~Boothby, J.~Burkert*, M.~Eichwald*, D.C.~Ernst, R.M.~Green, and M.~Macauley. On the Cyclically Fully Commutative Elements of Coxeter Groups.  \emph{J.~Algebraic Combin.}, 36(1), 2012.  [\href{http://arxiv.org/abs/1202.6657}{\texttt{arXiv:1202.6657}}]

\vspace{.25em}

\noindent D.C.~Ernst.  Non-cancellable elements in type affine $C$ Coxeter groups,  \emph{Int.~Electron.~J.~Algebra}, 8, 2010.  [\href{http://arxiv.org/abs/0910.0923}{\texttt{arXiv:0910.0923}}]

\vspace{.25em}

D.C.~Ernst.  Diagram calculus for a type affine $C$ Temperley--Lieb algebra, I. \emph{J.~Pure Appl.~Alg.}, 216(11), 2012. [\href{http://arxiv.org/abs/0910.0925}{\texttt{arXiv:0910.0925}}]

\vspace{.25em}

D.C.~Ernst. A diagrammatic representation of an affine $C$ Temperley–-Lieb algebra, PhD Thesis, University of Colorado, 2008. [\href{http://arxiv.org/abs/0905.4457}{\texttt{arXiv:0905.4457}}]

\end{enumerate}
 
\item[(d)] \textbf{Synergistic Activities}

Provost’s Award for Excellence in Undergraduate Inquiry \& Creativity \hfill Spring 2014\\
Award honors a faculty mentor who has demonstrated initiative, productivity, and dedication in contributing to the university community in the areas of research, scholarly, and/or creative activities.

\vspace{.25em}

Columnist for ``Math Ed Matters" \hfill Spring 2013--Present\\
Monthly column sponsored by the Mathematical Association of America. The column explores topics and current events related to undergraduate mathematics education. 

\vspace{.25em}

Special Projects Coordinator for Academy of Inquiry-Based Learning \hfill Fall 2012--Present\\
Help organize, promote, and run IBL-related events including workshops, special sessions, and conferences. Mentor for small cohort of mathematics instructors.  Includes annual stipend.

\vspace{.25em}

Member of Editorial Board for ``Math Horizons" \hfill Spring 2014--Present\\
Math Horizons is the undergraduate magazine of the Mathematical Association of America.

\vspace{.25em}

%Co-organizer for ``Inquiry-Based Learning Best Practices" \hfill Summer 2012, 2013\\
%MAA Contributed Paper Session, MathFest 2012, University of Wisconsin, Madison, WI.
%
%\vspace{.25em}

%Co-organizer for ``Combinatorics of Coxeter Groups" \hfill Spring 2011\\
%AMS Special Session, Spring 2011 Eastern Section Meeting of the AMS, College of the Holy Cross, Worcester, MA.
%
%\vspace{.25em}
 
Plymouth State University Distinguished Professor of Mathematics \hfill 2009 \& 2011\\
Teaching award determined by mathematics majors at Plymouth State University.

\item[(e)] \textbf{Collaborators and Other Affiliations} 
 
\begin{enumerate}[leftmargin=\parindent]
\item[(i)] \textbf{Collaborators \& Co-editors}

Tom Boothby (University of Washington), Jeffrey Burkert* (Harvey Mudd College), Morgan Eichwald* (University of Montana), Richard M.~Green (University of Colorado at Boulder), Angie Hodge (University of Nebraska at Omaha), Dane Jacobson* (Northern Arizona University), Matthew Macauley (Clemson University), Andrew Schultz (Wellesley College), N\'andor Sieben (Northern Arizona University)

%Tom Boothby (University of Washington), Jeffrey Burkert* (Harvey Mudd College), Joseph Cormier* (Plymouth State University), Ryan Cross* (Plymouth State University), Morgan Eichwald* (University of Montana), Selina Gilbertson* (Northern Arizona University), Richard M.~Green (University of Colorado at Boulder), Zachariah Goldenberg* (Plymouth State University), Katie Hills-Kimblall* (Plymouth State University), Angie Hodge (University of Nebraska at Omaha), Dane Jacobson* (Northern Arizona University), Jessica Kelly* (Plymouth State University), Matthew Macauley (Clemson University), Christopher Malbon* (Johns Hopkins), Christie Quaranta* (George Mason University), Andrew Schultz (Wellesley College), N\'andor Sieben (Northern Arizona University), Michael Woodward* (Northern Arizona University)

%P.~Gavin LaRose (University of Michigan)
%Spencer Shamblen (McDaniel College)
%Stan Yoshinobu (Cal Poly)
 
\item[(ii)] \textbf{Graduate and Postdoctoral Advisors}

PhD Advisor: Richard M.~Green (University of Colorado at Boulder).

MS Advisor: Michael J.~Falk (Northern Arizona University).

\item[(iii)] \textbf{MS Thesis Students}

Kirsten Davis (Northern Arizona University)

Brooke Fox (Northern Arizona University)

\end{enumerate}

\end{enumerate}

\end{document}