\documentclass[11pt]{article}

\usepackage{enumitem}
\usepackage[margin=1in]{geometry}

\linespread{1.2}

\begin{document}

\begin{center}
{\Large \textbf{Collaborative Research: Resource of Open\\
Problems for Education (ROPE)}}

\bigskip

{\Large Budget Justification}\\
\smallskip
Dana C.~Ernst
\end{center}

\begin{enumerate}[leftmargin=*]

\item[A.] \textbf{PERSONNEL}

PI Ernst requests one month's summer salary and the associated fringe benefits each year for 3 years. We have assumed a salary increase of 3\% per year.  During the funding period, the PI will work intensively on the specific tasks listed in the project description and other related items. 

\ \hfill \fbox{Subtotal: \$23,169}

\item[B.] \textbf{OTHER PERSONNEL}

None. \hfill \fbox{Subtotal: \$0}

\item[C.] \textbf{FRINGE BENEFITS}

Fringe benefits were calculated using NAU formulas for benefit rates for FY 2013 (19.9\%).

\hfill \fbox{Subtotal: \$4,611}

\item[D.] \textbf{EQUIPMENT}

None. \hfill \fbox{Subtotal: \$0}

\item[E.] \textbf{TRAVEL}

Travel funds are requested to allow the PI to attend national mathematics meetings to disseminate information about ROPE to allow for face-to-face team meetings.  Travel to the collaborative PIs' institutions is also planned for meetings with the Advisory Group and External Evaluator. In Years 2 and 3, funds are included to support undergraduate travel to the Joint Mathematical Meetings where they will have a demonstration of ROPE and help staff our booth in the exhibit area at the JMM.

\begin{enumerate}
\item[] \textbf{Year 1:} The PI is requesting a total of \$4,924.
\begin{itemize}
\item \$1,935 for travel to the Joint Mathematics Meetings to meet with PIs.
\begin{itemize}
\item \$240 Registration Fee
\item \$500 Airfare to San Antonio, TX
\item \$900 for lodging (\$225 per night for 4 nights)
\item \$245 for food (\$49 per diem rate for 5 days)
\end{itemize}

\item \$968 for travel to the the University of Michigan to meet with PIs and Advisory Group.
\begin{itemize}
\item \$600 Airfare to Ann Arbor, MI
\item \$200 for lodging (\$100 per night for 2 nights)
\item \$168 for food (\$56 per diem rate for 3 days)
\end{itemize}

\item \$2,021 for travel to MathFest to meet with PIs and External Evaluator.
\begin{itemize}
\item \$300 Registration Fee
\item \$750 Airfare to Washington, D.C.
\item \$735 for lodging (\$245 per night for 3 nights)
\item \$236 for food (\$59 per diem rate for 4 days)
\end{itemize}
\end{itemize}

\item[] \textbf{Year 2:} The PI is requesting a total of \$7,501.
\begin{itemize}
\item \$5,585 for travel to the Joint Mathematics Meetings to meet with PIs.
\begin{itemize}
\item \$240 Registration Fee for PI
\item \$110 Registration Fee for undergraduate students (\$55 student registration fee for two students)
\item \$1,650 Airfare to Seattle, WA (\$550 each for PI and two students)
\item \$2,700 for lodging (\$225 per night for 4 nights each for PI and two students)
\item \$885 for food (\$59 per diem rate for 5 days each for PI and two students)
\end{itemize}

\item \$1,916 for travel to MathFest to meet with PIs and External Evaluator.
\begin{itemize}
\item \$300 Registration Fee
\item \$750 Airfare to Columbus, OH.
\item \$690 for lodging (\$230 per night for 3 nights)
\item \$176 for food (\$44 per diem rate for 4 days)
\end{itemize}
\end{itemize}

\item[] \textbf{Year 3:} The PI is requesting a total of \$8,581.
\begin{itemize}
\item \$6,560 for travel to the Joint Mathematics Meetings to meet with PIs.
\begin{itemize}
\item \$240 Registration Fee for PI
\item \$110 Registration Fee for undergraduate students (\$55 student registration fee for two students)
\item \$2,250 Airfare to Atlanta, GA (\$750 each for PI and two students)
\item \$3,300 for lodging (\$275 per night for 4 nights each for PI and two students)
\item \$660 for food (\$59 per diem rate for 5 days each for PI and two students)
\end{itemize}

\item \$2,021 for travel to MathFest to meet with PIs and External Evaluator.
\begin{itemize}
\item \$300 Registration Fee
\item \$750 Airfare to East Coast (location currently unknown).
\item \$735 for lodging (\$245 per night for 3 nights)
\item \$236 for food (\$44 per diem rate for 4 days)
\end{itemize}
\end{itemize} 
\end{enumerate}

\hfill \fbox{Subtotal: \$21,006}

\item[F.] \textbf{PARTICIPANT SUPPORT COSTS}

None. \hfill \fbox{Subtotal: \$0}

\item[G.] \textbf{OTHER DIRECT COSTS}

None. \hfill \fbox{Subtotal: \$0}

\item[H.] \textbf{TOTAL DIRECT COSTS}

The total direct cost is the sum of summer salaries, fringe benefits, and travel for years 1--3. 

\hfill \fbox{Subtotal: \$48,786}

\item[I.] \textbf{INDIRECT COSTS}

Indirect costs are calculated based on Northern Arizona University's Colleges and Universities Rate Agreement, which stipulates an on-campus rate of 50\% MTDC in year 1 and 52\% in years 2 and 3, with exclusions for tuition, equipment, and subawards greater than \$25,000.

\ \hfill \fbox{Subtotal: \$25,091}

\item[J.] \textbf{TOTAL DIRECT AND INDIRECT COSTS}

This is the sum of items H and I. \hfill \fbox{\textbf{Total:} \$73,877}

\item[M.] \textbf{COST SHARING}

None. \hfill \fbox{Subtotal: \$0}

\end{enumerate}

\end{document}