\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}

\linespread{1.2}

\begin{document}
\begin{center}
{\Large \textbf{Collaborative Research: Resource of Open\\
Problems for Education (ROPE)}}
\end{center}

\begin{thebibliography}{9}

\bibitem{mathquest} Cline, Kelly, Mark Parker and Holly Zullo.
    ``MathQUEST/MathVote.'' On-line resource. 2012.  Carroll College.
    accessed 1/23/14.
    \texttt{<http://mathquest.carroll.edu/>}.

\bibitem{projectnext} MAA.  ``Project NExT.''  On-line information.  2014.
    accessed 9/18/14.\\
    \texttt{<http://projectnext.maa.org/>}.

\bibitem{webwork} The Mathematical Association of America.  ``WeBWorK.''
    Website.  2012.  accessed 1/23/14.
    \texttt{<http://webwork.maa.org/>}.

\bibitem{quadbase} Rice University.  ``Quadbase.''  On-line resource.
    Unknown authoring date.  accessed 1/23/14.
    \texttt{<http://quadbase.org/>}.

\bibitem{goodquestions} Terrell, Maria, Robert Connelly, David Henderson,
    and Robert Strichartz.  ``The GoodQuestions Project.''  On-line
    resource.  2005. Department of Mathematics, Cornell College.  accessed
    1/23/14.
    \texttt{<http://www.math.cornell.edu/$\sim$GoodQuestions/>}.

\bibitem{edfinity} ``Edfinity.''  Website.  2013.  accessed 1/23/14.
    \texttt{<http://edfinity.com/>}.

\bibitem{rlmooreconf} ``The Legacy of R.L. Moore---Events.''  The
  R.L. Moore Legacy Project.  Website, last revised 8/6/14.  accessed
  9/18/14. 
  \texttt{http://legacyrlmoore.org/events.html}

\bibitem{aibl} ``The Academy of Inquiry Based Learning.''
  Website.  accessed 9/18/14.\\
  \texttt{http://www.inquirybasedlearning.org/}

% \bibitem{latex2rtf} ``LaTeX to RTF Converter.''  Sourceforge repository.
%     Unknown authoring date;
%     updated 1/17/14.  accessed 1/23/14.
%     \texttt{<http://sourceforge.net/projects/latex2rtf/>}.
% http://imathas.com/index.html ?


\end{thebibliography}

\end{document}
